Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-17 paper/paper.tex
merging

\Fix{...listem 5 primeiras regras neste caso...}

\subsection{\Fix{JBoss JMX Console Beanshell Deployer WAR Upload and Deployment Exploit}}
\label{sec:jboss}
\label{sec:content-example}

>>>>

\begin{figure}[h]
  \vspace{-2ex}
  \lstinputlisting[language=C,numbers=none,frame=none,keywords={dsize,icode,itype,icmp\_id,icmp\_seq}]{top-pingscan.rules}
  \vspace{-3ex}  
\end{figure}

\Luc{Apenas 3 regras tiveram f1 de 100\%. O total de regras nesse caso foi de 13.}
\Fix{...listem 5 primeiras regras neste caso...}

\subsection{Remote Code Execution}
\label{sec:rce}
\label{sec:jboss}
\label{sec:content-example}

\Luc{"RCE refers to the process by which an agent can exploit a network vulnerability to run arbitrary code on a targeted machine or system. In an RCE attack, hackers intentionally exploit a remote code execution vulnerability to run malware. By prompting the targeted device to perform code execution, a hacker can run their own programming in its place. This programming can then enable them to gain full access, steal data, carry out a full distributed denial of service (DDoS) attack, destroy files and infrastructure, or engage in illegal activity. And as the term remote execution suggests, an RCE cyberattack can take place from any geophysical location."\\ Texto copiado de:  https://www.solarwindsmsp.com/blog/remote-code-execution \\
